Scaling rates of true polar wander in convecting planets and moons

### 2016-08-06 tpw_rate.tex
Add some more discussion.

\linenumbers

@@

Let $\delta$ be the size of the perturbation to the convective moment of inertia tensor after some time interval $\Delta t$, and let $\lambda_3 \ge \lambda_2 \ge \lambda_1$ be the eigenvalues of that tensor.  The corresponding rotation of the principal axes is defined by the angle $\xi$. A bound on $\xi$ is given by 
\begin{equation}
\vert \sin(2 \xi) \vert \le \frac{ 2 \vert \delta \vert}{ \displaystyle \min_{i \neq j} \vert \lambda_i - \lambda_j \vert }.
\label{eq:kahan}
\end{equation} 
That is to say, if there is a large difference between the eigenvalues, this stabilizes axes to perturbations.  
If, however, there is a small difference between the eigenvalues (i.e., they are nearly degenerate), then perturbations can cause large rotations of the principal axes.
This is illustrated schematically in Figure~\ref{fig:perturb}

@@

>>>>

%%\linenumbers

@@

Let $\delta$ be the size of the perturbation to the convective moment of inertia tensor after some time interval $\Delta t$, and let $\lambda_3 \ge \lambda_2 \ge \lambda_1$ be the eigenvalues of that tensor.  The corresponding rotation of the principal axes is defined by the angle $\xi$. A bound on $\xi$ is given by 
\begin{equation}
\vert \sin(2 \xi) \vert \le \frac{ 2 \vert \delta \vert}{ \displaystyle \min_{i \neq j} \vert \lambda_i - \lambda_j \vert }.
\label{eq:kahan}
\end{equation} 
That is to say, if there is a large difference between the eigenvalues, this stabilizes axes to perturbations.  
If, however, there is a small difference between the eigenvalues (i.e., they are nearly degenerate), then perturbations can cause large rotations of the principal axes.
This is illustrated schematically in Figure~\ref{fig:perturb}.
\citet{evans1998} described a situation where the convective moment of inertia of Earth is prolate, with the
maximum and intermediate moments of inertia nearly equal.
He argued that perturbations in this case would result in TPW paths that are approximately
on the great circle path between the intermediate and maximum axes.
This behavior is a consequence of the instability described in Equation~\eqref{eq:kahan}.

@@

\citet{tsai2007theoretical} suggested that interchanges in the principal moments are unlikely to produce large
TPW events, since (1) during an inertial interchange the total moment of inertia anomaly is small, and
(2) the TPW event can only asymptotically approach 90$^\circ$.
This is true for the case of a single interchange. However, we argue that this is overly restrictive
for our generalization of IITPW.
Our numerical experiments show that in a vigorously convecting system the principal moments can
interchange, or almost interchange, quite rapidly, and the perturbation sizes can be large soon after an interchange.
Furthermore, the location of the principal axes need not stay put during a TPW event,
which can lead to extended polar wandering of distances greater than 90$^\circ$.
